---
title: "Shiny shop"
author: "Aaron Berdanier"
date: "May 2, 2017"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float:
      collapsed: false
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Shiny building blocks

```{r eval=FALSE}
# R ENVIRONMENT
library(shiny)

# UI, this is a function call, so contents are elements = need commas between
ui <- fluidPage()

# SERVER, this is a function definition, so contents are objects
server <- function(input, output){}

shinyApp(ui = ui, server = server)
```

# Our components

## In the R environment

We want to load our packages, maybe set up some data, e.g.:

```
library(shiny)
library(leaflet)
library(googlesheets) # or library(rdrop2)
```

## In the UI

We want to include:

- site dropdown -- `selectInput()`
- number of widgets input -- `numericInput()`
- air temperature input -- `numericInput()`
- add data button -- `actionButton()`
- map with sites -- [leaflet](https://rstudio.github.io/leaflet/)
- graph with number v. temperature -- `plotOutput()`
- table with date, site, number, Temperature -- `tableOutput()` or `dataTableOutput()`
- download .csv button -- `downloadButton()`

## In the Server

We want to include:

- sites data -- maybe a `list()`?
- "add data" processing -- [google drive sheet](https://github.com/jennybc/googlesheets) or [dropbox file](https://github.com/karthik/rdrop2)
- render leaflet -- [leaflet](https://rstudio.github.io/leaflet/)
- render graph -- `renderPlot()`
- render table -- `renderTable()` or `DT::renderDataTable()`
- render download -- [`downloadHandler()`](http://shiny.rstudio.com/gallery/file-download.html)

# Our development steps

1. Set up basic interface, spit out inputs in a table -- test
2. Set up data interface with google sheets -- test
3. Set up leaflet interface -- test
4. Combine them -- test

## 1. Basic interface

#### See above. For now, make it just output user input into a table -- **test**

## 2. google sheets integration

#### We need to **authenticate our google access** first. 
We only do this once, and *do not* copy the code into our shiny app.R

```
library(googlesheets)
shiny_token <- gs_auth() # authenticate
saveRDS(shiny_token, "shiny_app_token.rds")
initial_sheet <- data.frame(addtime=0, site=0, weather=0, nwidgets=0)
 # need to set up with our columns...
ss <- gs_new("my-shiny-database", input=initial_sheet)
ss$sheet_key # like: "10kYZGTfXquVUwvBXH-8M-p01csXN6MNuuTzxnDdy3Pk"
```

**NOTE:** add `*.rds` and `.httr-oauth` to .gitignore if using git!

#### Then, we can push and get data -- **test**

```
googlesheets::gs_auth(token = "shiny_app_token.rds")

sheetkey <- "10kYZGTfXquVUwvBXH-8M-p01csXN6MNuuTzxnDdy3Pk"
ss <- googlesheets::gs_key(sheetkey)
# OR THIS
# mytable <- "my-shiny-database"
# ss <- googlesheets::gs_table(mytable)

save_gdata <- function(data){
  googlesheets::gs_add_row(ss, input = data)
}
load_gdata <- function(){
  googlesheets::gs_read_csv(ss)
}
```
(modified from [Dean Attali](http://deanattali.com/blog/shiny-persistent-data-storage/#gsheets))

## 3. leaflet interface

#### A basic map -- **test**

```
library(leaflet)
m <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
m  # Print the map
```
(from [RStudio](https://rstudio.github.io/leaflet/))

#### Then, we can [add a leaflet map to Shiny](https://rstudio.github.io/leaflet/shiny.html)...

## 4. Put it together

#### Some pseudocode -- **Actions and reactions**

* User clicks add data button
    + server adds data to database (on google sheets?)
    + redraw data table
    + redraw graph
* User clicks on a site on the map
    + filter table data
    + filter graph data
* User clicks on download data button
    + grab data in data table
    + download to file

